% !TEX root = report.tex

\section{Related Work}
\label{sec:related_work}

\subsection{Fine-Grained Visual Categorization}

FGVC has been studied extensively for birds~\cite{WahCUB2002011}, aircraft, and vehicles. Early approaches relied on part-based models and hand-crafted features, and required explicit part annotations at training time. Current methods use deep CNNs with attention to localize discriminative regions without manual supervision, which improves both accuracy and scalability.

\subsection{The CompCars Dataset}

Yang et al.~\cite{Yang2015} introduced CompCars, a large-scale car dataset for fine-grained categorization and verification, with web-nature and surveillance-nature images annotated hierarchically by make, model, and year. Using OverFeat features with multi-view fusion they reported 82.9\% on make classification and 76.7\% on model classification. That result is the primary baseline here, and the hierarchical annotation is what makes the multi-task formulation of \secref{sec:architectures} possible.

\subsection{Deep CNN Architectures}

ResNet~\cite{He2016} introduced skip connections that allow very deep networks to train without gradient degradation, and the residual formulation scales to hundreds of layers while remaining trainable.

EfficientNet~\cite{Tan2019} uses compound scaling to jointly optimize depth, width, and resolution through neural architecture search. It reaches a better accuracy-to-parameter ratio, with EfficientNet-B0 matching ResNet50 accuracy using 6$\times$ fewer parameters. Both architectures gain substantially from transfer learning on domain-specific tasks with limited data.

\subsection{Attention Mechanisms}

Squeeze-and-Excitation Networks~\cite{Hu2018} apply channel attention: global average pooling followed by fully-connected layers that recalibrate channel-wise feature responses. Modelling channel interdependence explicitly lets a network emphasize informative channels and suppress the rest. For fine-grained classification this is directly useful, since the discriminative evidence sits in narrow visual details such as grilles, headlights, and body contours.

\subsection{Transfer Learning}

Pretraining on ImageNet~\cite{Deng2009} and fine-tuning on the target domain is standard for recognition tasks with limited training data. The learned features transfer across domains and supply both a better initialization and implicit regularization. Differential learning rates (lower for pretrained layers, higher for new classifier heads) preserve the learned representation while the task-specific layers adapt.
