\documentclass[10pt, conference, letterpaper]{IEEEtran}

\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[ansinew]{inputenc}
\usepackage{xcolor}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{import}
\usepackage{multirow}
\usepackage{cite}
\usepackage[export]{adjustbox}
\usepackage{breqn}
\usepackage{mathrsfs}
\usepackage{acronym}
\usepackage{setspace}
\usepackage{bm}
\usepackage{stackengine}
\usepackage{booktabs}

\graphicspath{{./figures/}}
\setlength{\belowcaptionskip}{0mm}
\setlength{\textfloatsep}{8pt}

\newcommand{\eq}[1]{Eq.~\eqref{#1}}
\newcommand{\fig}[1]{Fig.~\ref{#1}}
\newcommand{\tab}[1]{Tab.~\ref{#1}}
\newcommand{\secref}[1]{Section~\ref{#1}}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

\setlength{\columnsep}{0.2in}

\title{Fine-Grained Car Make Classification Using Convolutional Neural Networks with Hierarchical Multi-Task Learning}

\author{Alexandru Mihailescu\thanks{Work done for the course of Neural Networks and Deep Learning, taught by Prof. Jacopo Pegoraro and Prof. Michele Rossi at the University of Padua.}}

\IEEEoverridecommandlockouts

\begin{document}

\maketitle

\begin{abstract}
Fine-grained visual categorization of automobiles has applications in autonomous driving, intelligent transportation, surveillance, and insurance claim processing. This report compares convolutional neural network architectures for car make classification on the CompCars classification split, 30,955 images across 75 makes and 431 models. Five models are evaluated: a baseline CNN trained from scratch, ResNet50, EfficientNet-B0, ResNet50 augmented with Squeeze-and-Excitation attention, and a hierarchical multi-task network that predicts make (75 classes) and model (431 classes) from a shared backbone with dual heads. The hierarchical network is the best model, reaching 87.55\% top-1 make accuracy and 82.72\% top-1 model accuracy on the test split, which exceeds the OverFeat baseline of Yang et al. by 4.65 and 6.02 percentage points respectively; its second head costs nothing at inference. Transfer learning from ImageNet is the dominant factor: pretrained backbones reach 80\% to 88\% test accuracy against 53.08\% from scratch. SE attention adds 1.79 points over ResNet50 for 0.7M parameters, and EfficientNet-B0 reaches 86.95\% with 4.1M parameters at twice the throughput of any ResNet50 variant. Focal loss does not help despite a 120:1 class imbalance, losing 1.89 points to cross-entropy. Every model loses 10 to 22 accuracy points between the random validation split and the official test split, so validation accuracy on this benchmark is a model-selection signal and not a performance estimate.
\end{abstract}

\IEEEkeywords
Fine-Grained Classification, Convolutional Neural Networks, Transfer Learning, Attention Mechanisms, Multi-Task Learning, Vehicle Recognition.
\endIEEEkeywords

\input{intro}

\input{related}

\input{model}

\input{results}

\input{conclusions}

\bibliography{biblio}
\bibliographystyle{ieeetr}

\end{document}
